Fusing Filters with Integer Linear Programming

### 2014-05-15 2014betterfusionforfilters/Main.tex
Cut back the ILP intro
change sigplan category; I think compilers/optimization more fitting

@@

\begin{abstract}
Minimising memory traffic is key to compiling functional, collection oriented array programs into efficient code.
It is not sufficient to simply fuse subsequent array operations into a single computation; we also have to cluster \emph{separate} traversals of the same array into a single loop.
Previous work demonstrated how Integer Linear Programming (ILP) can be used to cluster the operators in a general data-flow graph into subgraphs, which can be individually fused.
However, these approaches can only handle operations which preserve the size of the array, thereby missing out on some optimisation opportunities.
This paper addresses this shortcoming by extending the ILP approach with support for size-changing operations, using an external ILP solver to find good clusterings.
\end{abstract}

\category
	{D.3.3}
	{Programming Languages}
	{Language Constructs and Features---Concurrent programming structures; Control structures; Abstract data types}

>>>>

% \TODO{Put this somewhere: Fusion-preventing dependencies are akin to barrier synchronisations in the Bulk Synchronous model of parallel computation. }

@@

\begin{abstract}
Minimising memory traffic is key to compiling functional, collection-oriented array programs into efficient code.
It is not sufficient to simply fuse subsequent array operations into a single computation; we also have to cluster \emph{separate} traversals of the same array into a single loop.
Previous work demonstrated how Integer Linear Programming (ILP) can be used to cluster the operators in a general data-flow graph into subgraphs, which can be individually fused.
However, these approaches can only handle operations which preserve the size of the array, thereby missing out on some optimisation opportunities.
This paper addresses this shortcoming by extending the ILP approach with support for size-changing operations, using an external ILP solver to find good clusterings.
\end{abstract}

\category
	{D.3.4}
	{Programming Languages}
	{Processors---Compilers; Optimization}
